When Do You Repeat Yourself?\\ Voices from the Trenches of Linux Kernel Maintainers on Code Duplication

### 2025-10-29 papers/techdebt2026/techdebt.tex
techdebt2026: techdebt: include a quote for Group 10 and takeaway T4
The patch from Group 10 produced an interesting quote related to
takeaway T4, which is not present in the paper. Given that we have quite
a few space left, include it.

Signed-off-by: David Tadokoro <davidbtadokoro@usp.br>

In the interaction of Group 10, there was also a hint that performance could be considered when evaluating the merit of a deduplication. Nonetheless, this notion surfaced aggressively with Group 9, where the contribution could completely remove both duplicated functions using the inline method by leveraging helpers; however, one of the functions had a call that, if eliminated, would result in a significant performance impact: \textit{``Note that is not an appropriate change for the large reads though [...] This is the one case were \texttt{spi\_write\_then\_read()} is probably not appropriate due to the large buffers that are potentially involved.''}. These interactions, coupled with the low-level development context of Linux and driver development, which is usually related to devices with limited resources, produced our fourth and final takeaway.

>>>>

In the interaction of Group 10, there was also a hint that performance could be considered when evaluating the worth of a deduplication, whilst reaffirming that readability was a priority in that context: \textit{``I'd be slightly interested to see the optimized output of the two approaches, but this is far from a high performance path so we care a lot more about readability here.''}. Nonetheless, this notion surfaced aggressively with Group 10, where the contribution could completely remove both duplicated functions using the inline method by leveraging helpers; however, one of the functions had a call that, if eliminated, would result in a significant performance impact: \textit{``Note that is not an appropriate change for the large reads though [...] This is the one case were \texttt{spi\_write\_then\_read()} is probably not appropriate due to the large buffers that are potentially involved.''}. These interactions, coupled with the low-level development context of Linux and driver development, which is usually related to devices with limited resources, produced our fourth and final takeaway:
